The POSIX time standard

### 2024-07-06 text/21/zero-inflated-poisson.Rmd
Updated 2022 Rmd files

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

@@

```{r setup}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(pscl)))
```

@@

```{r, eval=FALSE}
fn <- "http://faculty.missouri.edu/huangf/data/poisson/articles.csv"
articles <- read.csv(fn)
head(articles)
```

@@

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r}
pois1 %>%
  tidy %>%
  mutate(lower_limit=estimate-1.96*std.error) %>%
  mutate(upper_limit=estimate+1.96*std.error) %>%
  select(term, estimate, lower_limit, upper_limit) %>%
  mutate(estimate=exp(estimate)) %>%
  mutate(lower_limit=exp(lower_limit)) %>%
  mutate(upper_limit=exp(upper_limit)) -> pois1_coefficients
pois1_coefficients
```

@@

```{r}
zip1 <- zeroinfl(art ~ fem + ment + phd + mar + kid5 | 1, family=poisson, data = articles)
summary(zip1)
```

>>>>

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
- Incomplete page
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r zero-inflated-poisson-01}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(pscl)))
```

@@

```{r zero-inflated-poisson-02, eval=FALSE}
fn <- "http://faculty.missouri.edu/huangf/data/poisson/articles.csv"
articles <- read.csv(fn)
head(articles)
```

@@

```{r zero-inflated-poisson-03}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r zero-inflated-poisson-04}
pois1 %>%
  tidy %>%
  mutate(lower_limit=estimate-1.96*std.error) %>%
  mutate(upper_limit=estimate+1.96*std.error) %>%
  select(term, estimate, lower_limit, upper_limit) %>%
  mutate(estimate=exp(estimate)) %>%
  mutate(lower_limit=exp(lower_limit)) %>%
  mutate(upper_limit=exp(upper_limit)) -> pois1_coefficients
pois1_coefficients
```

@@

```{r zero-inflated-poisson-05}
zip1 <- zeroinfl(art ~ fem + ment + phd + mar + kid5 | 1, family=poisson, data = articles)
summary(zip1)
```

### 2024-07-06 text/22/analysis-of-means.Rmd
Updated 2022 Rmd files

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
page_update: complete
---

@@

```{r, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[j] ~ " for all i,j")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu ~ " for all i=1,...,k")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r, echo=FALSE}
mn <- c(
  21.83,
  20.40,
  21.62,
  21.06,
  20.57)

@@

```{r, echo=FALSE}
# Make the numbers look nice
ybarbar <- round(ybarbar, 2)
mse <- round(mse, 2)
lo <- round(lo, 2)
hi <- round(hi, 2)
```

>>>>

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: 
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

@@

```{r analysis-of-means-01, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[j] ~ " for all i,j")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r analysis-of-means-02, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu ~ " for all i=1,...,k")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r analysis-of-means-03, echo=FALSE}
mn <- c(
  21.83,
  20.40,
  21.62,
  21.06,
  20.57)

@@

```{r analysis-of-means-04, echo=FALSE}
# Make the numbers look nice
ybarbar <- round(ybarbar, 2)
mse <- round(mse, 2)
lo <- round(lo, 2)
hi <- round(hi, 2)
```

### 2024-07-06 text/22/box-with-no-whiskers.Rmd
Updated 2022 Rmd files

```{r, fig.height=1.5, echo=FALSE}
suppressMessages(suppressWarnings(library(tidyverse)))
n1 <- 10
n2 <- 10
pseudo_boxplot <- function(n1, n2, a1, b1, a2, b2) {
  x1 <- qbeta((1:n1)/(n1+1), 6, 2)
  x2 <- qbeta((1:n2)/(n2+1), 5, 3)
  data.frame(x=c(x1, x2), g=paste0("g", rep(1:2, c(n1, n2)))) -> df
  print(df)
  df %>%
    ggplot(aes(g, x)) +
      geom_boxplot() +
      coord_flip()
}

@@

```{r, fig.height=1.5, echo=FALSE}
pseudo_boxplot(10, 2, 6, 2, 5, 3)
```

>>>>

```{r box-with-no-whiskers-01, fig.height=1.5, echo=FALSE}
suppressMessages(suppressWarnings(library(tidyverse)))
n1 <- 10
n2 <- 10
pseudo_boxplot <- function(n1, n2, a1, b1, a2, b2) {
  x1 <- qbeta((1:n1)/(n1+1), 6, 2)
  x2 <- qbeta((1:n2)/(n2+1), 5, 3)
  data.frame(x=c(x1, x2), g=paste0("g", rep(1:2, c(n1, n2)))) -> df
  print(df)
  df %>%
    ggplot(aes(g, x)) +
      geom_boxplot() +
      coord_flip()
}

@@

```{r box-with-no-whiskers-02, fig.height=1.5, echo=FALSE}
pseudo_boxplot(10, 2, 6, 2, 5, 3)
```

### 2024-07-06 text/22/definition-schoenfeld-residuals.Rmd
Updated 2022 Rmd files

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags: Survival analysis
source: new
---

@@

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
suppressMessages(suppressWarnings(library(plot3D)))
```

```{r}
library(plot3D)

@@

>>>>>>> 17772f400cc3acd5b2c61623fc3cf2c98df50124

>>>>

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags:
- Rmarkdown code
- Survival analysis
source: new
page_update: complete
---

@@

```{r definition-schoenfeld-residuals-01, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
suppressMessages(suppressWarnings(library(plot3D)))
```

```{r definition-schoenfeld-residuals-02}
library(plot3D)

@@

### 2024-07-06 text/22/different-parameterizations.Rmd
Updated 2022 Rmd files

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
category: 
- Blog post
tags:
- Analysis of variance
output: html_document
page_update: complete
---

@@

```{r setup}
library(MASS)
library(matlib)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
means <- c(52, 54, 62, 72)
mean(means)
y <- 
  rep(means, each=3) +
  rep(c(0, 1, -1), 4)
g <- rep(1:4, each=3)
df <- cbind(g, y)
```

@@

```{r}
data.frame(g, y) %>%
  group_by(g) %>%
  summarize(mean_y=mean(y))
```

@@

```{r}
x1 <- as.numeric(g==1)
x2 <- as.numeric(g==2)
x3 <- as.numeric(g==3)
x4 <- as.numeric(g==4)
```

@@

```{r}
A <- cbind(x1, x2, x3, x4) 
A
```

@@

```{r}
beta_A <- coef(lm(y~x1+x2+x3+x4-1))
beta_A
```

@@

```{r}
inv(t(A)%*%A)%*%t(A) %>% fractions
```

@@

```{r}
x0 <- rep(1, 12)
x1 <- as.numeric(g==2)
x2 <- as.numeric(g==3)
x3 <- as.numeric(g==4)

@@

```{r}
B <- cbind(x0, x1, x2, x3) 
B
```

@@

```{r}
beta_B <- coef(lm(y~x0+x1+x2+x3-1))
beta_B
```

```{r}
inv(t(B)%*%B)%*%t(B) %>% fractions
```

@@

```{r}
B[1:3, ]
```

@@

```{r}
B[4:6, ]
```

@@

```{r}
x0 <- rep(1, 12)
x1 <- as.numeric(g==2) - as.numeric(g==1)
x2 <- as.numeric(g==3) - as.numeric(g==1)
x3 <- as.numeric(g==4) - as.numeric(g==1)
```

@@

```{r}
D <- cbind(x0, x1, x2, x3) 
D
```

@@

```{r}
beta_D <- coef(lm(y~x0+x1+x2+x3-1))
beta_D
```

```{r}
inv(t(D)%*%D)%*%t(D) %>% fractions
```

@@

```{r}
B
```

@@

```{r, echo=FALSE}
V <- matrix(c(
  1,  0,  0,  0,
  1,  1,  0,  0,
  1,  0,  1,  0,
  1,  0,  0,  1), nrow=4, byrow=TRUE)
V
```

@@

```{r}
A%*%V
```

@@

```{r}
U=inv(V)
U
```

@@

```{r}
B%*%U
```

@@

```{r}
beta_A
```

```{r}
beta_B
```

```{r}
inv(V)%*%beta_A
```

@@

```{r}
V%*%beta_B
```

@@

@@

```{r}
D
```

@@

```{r, echo=FALSE}
V <- matrix(c(
  1, -1, -1, -1,
  1,  1,  0,  0,
  1,  0,  1,  0,
  1,  0,  0,  1), nrow=4, byrow=TRUE)
V
```

@@

```{r}
A%*%V
```

@@

```{r}
U=inv(V)
U
```

```{r}
D%*%U
```

@@

```{r}
beta_A
```

@@

```{r}
beta_D
```

@@

```{r}
inv(V)%*%beta_A
```

@@

```{r}
V%*%beta_D
```

@@

```{r, echo=FALSE}
U <- matrix(c(
  1,  0,  0,  0,
 -1,  1,  0,  0,
  0, -1,  1,  0,
  0,  0, -1,  1), nrow=4, byrow=TRUE)
U
```

@@

@@

```{r}
V <- inv(U)
V
```

@@

```{r}
E <- A%*%inv(U)
E
```

@@

```{r}
x0 <- E[ , 1]
x1 <- E[ , 2]
x2 <- E[ , 3]
x3 <- E[ , 4]
beta_E <- coef(lm(y~x0+x1+x2+x3-1))
beta_E
```

>>>>

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
category: 
- Blog post
tags:
- Analysis of variance
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r different-parameterizations-01}
library(MASS)
library(matlib)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r different-parameterizations-02}
means <- c(52, 54, 62, 72)
mean(means)
y <- 
  rep(means, each=3) +
  rep(c(0, 1, -1), 4)
g <- rep(1:4, each=3)
df <- cbind(g, y)
```

@@

```{r different-parameterizations-03}
data.frame(g, y) %>%
  group_by(g) %>%
  summarize(mean_y=mean(y))
```

@@

```{r different-parameterizations-04}
x1 <- as.numeric(g==1)
x2 <- as.numeric(g==2)
x3 <- as.numeric(g==3)
x4 <- as.numeric(g==4)
```

@@

```{r different-parameterizations-05}
A <- cbind(x1, x2, x3, x4) 
A
```

@@

```{r different-parameterizations-06}
beta_A <- coef(lm(y~x1+x2+x3+x4-1))
beta_A
```

@@

```{r different-parameterizations-07}
inv(t(A)%*%A)%*%t(A) %>% fractions
```

@@

```{r different-parameterizations-08}
x0 <- rep(1, 12)
x1 <- as.numeric(g==2)
x2 <- as.numeric(g==3)
x3 <- as.numeric(g==4)

@@

```{r different-parameterizations-09}
B <- cbind(x0, x1, x2, x3) 
B
```

@@

```{r different-parameterizations-10}
beta_B <- coef(lm(y~x0+x1+x2+x3-1))
beta_B
```

```{r different-parameterizations-11}
inv(t(B)%*%B)%*%t(B) %>% fractions
```

@@

```{r different-parameterizations-12}
B[1:3, ]
```

@@

```{r different-parameterizations-13}
B[4:6, ]
```

@@

```{r different-parameterizations-14}
x0 <- rep(1, 12)
x1 <- as.numeric(g==2) - as.numeric(g==1)
x2 <- as.numeric(g==3) - as.numeric(g==1)
x3 <- as.numeric(g==4) - as.numeric(g==1)
```

@@

```{r different-parameterizations-15}
D <- cbind(x0, x1, x2, x3) 
D
```

@@

```{r different-parameterizations-16}
beta_D <- coef(lm(y~x0+x1+x2+x3-1))
beta_D
```

```{r different-parameterizations-17}
inv(t(D)%*%D)%*%t(D) %>% fractions
```

@@

```{r different-parameterizations-18}
B
```

@@

```{r different-parameterizations-19, echo=FALSE}
V <- matrix(c(
  1,  0,  0,  0,
  1,  1,  0,  0,
  1,  0,  1,  0,
  1,  0,  0,  1), nrow=4, byrow=TRUE)
V
```

@@

```{r different-parameterizations-20}
A%*%V
```

@@

```{r different-parameterizations-21}
U=inv(V)
U
```

@@

```{r different-parameterizations-22}
B%*%U
```

@@

```{r different-parameterizations-23}
beta_A
```

```{r different-parameterizations-24}
beta_B
```

```{r different-parameterizations-25}
inv(V)%*%beta_A
```

@@

```{r different-parameterizations-26}
V%*%beta_B
```

@@

```{r different-parameterizations-27}
A
```

@@

```{r different-parameterizations-28}
D
```

@@

```{r different-parameterizations-29, echo=FALSE}
V <- matrix(c(
  1, -1, -1, -1,
  1,  1,  0,  0,
  1,  0,  1,  0,
  1,  0,  0,  1), nrow=4, byrow=TRUE)
V
```

@@

```{r different-parameterizations-30}
A%*%V
```

@@

```{r different-parameterizations-31}
U=inv(V)
U
```

```{r different-parameterizations-32}
D%*%U
```

@@

```{r different-parameterizations-33}
beta_A
```

@@

```{r different-parameterizations-34}
beta_D
```

@@

```{r different-parameterizations-35}
inv(V)%*%beta_A
```

@@

```{r different-parameterizations-36}
V%*%beta_D
```

@@

```{r different-parameterizations-37, echo=FALSE}
U <- matrix(c(
  1,  0,  0,  0,
 -1,  1,  0,  0,
  0, -1,  1,  0,
  0,  0, -1,  1), nrow=4, byrow=TRUE)
U
```

@@

```{r different-parameterizations-38}
A
```

@@

```{r different-parameterizations-39}
V <- inv(U)
V
```

@@

```{r different-parameterizations-40}
E <- A%*%inv(U)
E
```

@@

```{r different-parameterizations-41}
x0 <- E[ , 1]
x1 <- E[ , 2]
x2 <- E[ , 3]
x3 <- E[ , 4]
beta_E <- coef(lm(y~x0+x1+x2+x3-1))
beta_E
```

### 2024-07-06 text/22/dunnetts-test.Rmd
Updated 2022 Rmd files

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
---

@@

```{r, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[j] ~ " for all i,j")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[1] ~ " for all i=2,...,k")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r, echo=FALSE, comment=""}
mn1 <- c(21.39, 22.58, 16.94, 21.93, 19.93, 22.00)
sd1 <- c( 3.35,  2.88,  3.50,  3.05,  1.86, 3.71)
data.frame(mean=mn1, standard_deviation=sd1)
```

```{r, echo=FALSE, comment=""}
suppressMessages(suppressWarnings(library(tidyverse)))
mse <- mean(sd1^2)
d <- 2.73
n <- 20
lo <- mn1[1] - d*sqrt(2*mse/20)
hi <- mn1[1] + d*sqrt(2*mse/20)
```

@@

```{r, echo=FALSE, comment=""}
data.frame(g=2:6, mn=mn1[-1]) %>%
  ggplot(aes(g, mn)) +
    geom_point() +
    geom_segment(
      x=2:6, 
      xend=2:6, 
      y=mn1[-1], 
      yend=mn1[1]) +
    geom_segment(x=1.9, y=lo, xend=6.1, yend=lo) +
    geom_segment(x=1.9, y=hi, xend=6.1, yend=hi) +
    geom_segment(x=1.9, y=mn1[1], xend=6.1, yend=mn1[1], lty="dotted") +
    expand_limits(y=c(16, 26)) +
    expand_limits(x=c(0.9, 6.1)) +
    xlab("Disinfection protocol") +
    ylab("Tensile strength") +
    scale_x_continuous(breaks=1:6, minor_breaks=NULL) +
    scale_y_continuous(breaks=2*(8:13))
```

@@

```{r echo=FALSE}
# Make the numbers look nice.
mse <- round(mse, 2)
lo <- round(lo, 2)
hi <- round(hi, 2)
```

>>>>

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags:
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

@@

```{r dunnetts-test-01, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[j] ~ " for all i,j")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r dunnetts-test-02, fig.width=5, fig.height=0.33, echo=FALSE}
h0 <- bquote(H[0] ~ ": " ~ mu[i] == mu[1] ~ " for all i=2,...,k")
par(mar=rep(0.1, 4))
plot(0:1, 0:1, axes=FALSE, type="n")
text(0.1, 0.5, h0, adj=0)
```

@@

```{r dunnetts-test-03, echo=FALSE, comment=""}
mn1 <- c(21.39, 22.58, 16.94, 21.93, 19.93, 22.00)
sd1 <- c( 3.35,  2.88,  3.50,  3.05,  1.86, 3.71)
data.frame(mean=mn1, standard_deviation=sd1)
```

```{r dunnetts-test-04, echo=FALSE, comment=""}
suppressMessages(suppressWarnings(library(tidyverse)))
mse <- mean(sd1^2)
d <- 2.73
n <- 20
lo <- mn1[1] - d*sqrt(2*mse/20)
hi <- mn1[1] + d*sqrt(2*mse/20)
```

@@

```{r dunnetts-test-05, echo=FALSE, comment=""}
data.frame(g=2:6, mn=mn1[-1]) %>%
  ggplot(aes(g, mn)) +
    geom_point() +
    geom_segment(
      x=2:6, 
      xend=2:6, 
      y=mn1[-1], 
      yend=mn1[1]) +
    geom_segment(x=1.9, y=lo, xend=6.1, yend=lo) +
    geom_segment(x=1.9, y=hi, xend=6.1, yend=hi) +
    geom_segment(x=1.9, y=mn1[1], xend=6.1, yend=mn1[1], lty="dotted") +
    expand_limits(y=c(16, 26)) +
    expand_limits(x=c(0.9, 6.1)) +
    xlab("Disinfection protocol") +
    ylab("Tensile strength") +
    scale_x_continuous(breaks=1:6, minor_breaks=NULL) +
    scale_y_continuous(breaks=2*(8:13))
```

@@

```{r dunnetts-test-06, echo=FALSE}
# Make the numbers look nice.
mse <- round(mse, 2)
lo <- round(lo, 2)
hi <- round(hi, 2)
```

### 2024-07-06 text/22/mapping-longitude-latitude.Rmd
Updated 2022 Rmd files

```{r usa-map}
library(maps); library(ggplot2); library(mapproj)
states <- map_data("state")
usamap <- ggplot(states, aes(x=long, y=lat, group=group)) +
  geom_polygon(fill="white", colour="black")
usamap + coord_map("mercator")
usamap + coord_map("azequalarea") 
```

@@

```{r peek}
head(states)
```

@@

```{r plot3d}
library(dplyr)
library(magrittr)
library(plot3D)
draw_arc <- function(lon=c(0, 360), lat=c(-90, 90), co="black") {
  n <- 100
  if (length(lon)==1) {lon <- rep(lon, 2)}
  if (length(lat)==1) {lat <- rep(lat, 2)}
  lon <- seq(lon[1], lon[2], length=n)*pi/180
  lat <- seq(lat[1], lat[2], length=n)*pi/180
  # formulas from 
  #  https://en.wikipedia.org/wiki/Spherical_coordinate_system
  #  but swap theta and phi. Also lat=90-phi.
  x <- cos(lat)*cos(lon)
  y <- cos(lat)*sin(lon)
  z <- sin(lat)
  segments3D(
    x[-n], y[-n], z[-n], 
    x[-1], y[-1], z[-1], 
    box=FALSE, add=TRUE, col=co)
}
# Draw some "invisible" points to assure a full view of the arcs.
a <- c(-1, 1)
a_grid <- sapply(mesh(a, a, a), as.vector)
scatter3D(
  a_grid[ , 1], 
  a_grid[ , 2], 
  a_grid[ , 3], 
  col="white", 
  box=FALSE)  
for (lat in (-8:8)*10) {draw_arc(lat=lat, co="gray90")}
for (lon in (1:18)*20) {draw_arc(lon=lon, co="gray90")}
draw_arc(lat= 0, co="black")
draw_arc(lat=40, co="red")
```

@@

```{r square}
scatter3D(
  a_grid[ , 1], 
  a_grid[ , 2], 
  a_grid[ , 3], 
  col="white", 
  box=FALSE)  
for (lat in (-8:8)*10) {draw_arc(lat=lat, co="gray90")}
for (lon in (1:18)*20) {draw_arc(lon=lon, co="gray90")}
draw_arc(lon=280, lat=c(40, 60), co="darkgreen")
draw_arc(lon=320, lat=c(40, 60), co="darkgreen")
draw_arc(lon=c(280, 320), lat=40, co="darkgreen")
draw_arc(lon=c(280, 320), lat=60, co="darkgreen")
```

>>>>

```{r mapping-longitude-latitude-01}
library(maps); library(ggplot2); library(mapproj)
states <- map_data("state")
usamap <- ggplot(states, aes(x=long, y=lat, group=group)) +
  geom_polygon(fill="white", colour="black")
usamap + coord_map("mercator")
usamap + coord_map("azequalarea") 
```

@@

```{r mapping-longitude-latitude-02}
head(states)
```

@@

```{r mapping-longitude-latitude-03}
library(dplyr)
library(magrittr)
library(plot3D)
draw_arc <- function(lon=c(0, 360), lat=c(-90, 90), co="black") {
  n <- 100
  if (length(lon)==1) {lon <- rep(lon, 2)}
  if (length(lat)==1) {lat <- rep(lat, 2)}
  lon <- seq(lon[1], lon[2], length=n)*pi/180
  lat <- seq(lat[1], lat[2], length=n)*pi/180
  # formulas from 
  #  https://en.wikipedia.org/wiki/Spherical_coordinate_system
  #  but swap theta and phi. Also lat=90-phi.
  x <- cos(lat)*cos(lon)
  y <- cos(lat)*sin(lon)
  z <- sin(lat)
  segments3D(
    x[-n], y[-n], z[-n], 
    x[-1], y[-1], z[-1], 
    box=FALSE, add=TRUE, col=co)
}
# Draw some "invisible" points to assure a full view of the arcs.
a <- c(-1, 1)
a_grid <- sapply(mesh(a, a, a), as.vector)
scatter3D(
  a_grid[ , 1], 
  a_grid[ , 2], 
  a_grid[ , 3], 
  col="white", 
  box=FALSE)  
for (lat in (-8:8)*10) {draw_arc(lat=lat, co="gray90")}
for (lon in (1:18)*20) {draw_arc(lon=lon, co="gray90")}
draw_arc(lat= 0, co="black")
draw_arc(lat=40, co="red")
```

@@

```{r mapping-longitude-latitude-04}
scatter3D(
  a_grid[ , 1], 
  a_grid[ , 2], 
  a_grid[ , 3], 
  col="white", 
  box=FALSE)  
for (lat in (-8:8)*10) {draw_arc(lat=lat, co="gray90")}
for (lon in (1:18)*20) {draw_arc(lon=lon, co="gray90")}
draw_arc(lon=280, lat=c(40, 60), co="darkgreen")
draw_arc(lon=320, lat=c(40, 60), co="darkgreen")
draw_arc(lon=c(280, 320), lat=40, co="darkgreen")
draw_arc(lon=c(280, 320), lat=60, co="darkgreen")
```

### 2024-07-06 text/22/posix-time.Rmd
Updated 2022 Rmd files

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags: Data science
source: new
---

@@

```{r}
date_string <- "1970-01-01"
date_internal_r_format <- as.Date(date_string)
date_posix_ct <- as.POSIXct(date_string)
date_posix_lt <- as.POSIXlt(date_string)

@@

```{r}
print.default(date_string)
```

@@

```{r}
print.default(date_internal_r_format)
```

@@

```{r}
print.default(date_posix_ct)
```

@@

```{r}
print.default(date_posix_lt)
```

@@

```{r}
date_internal_r_format <- as.Date(1, origin="1970-01-01")
date_posix_ct <- as.POSIXct(86400, origin="1970-01-01")
date_posix_lt <- as.POSIXlt(86400, origin="1970-01-01")

@@

```{r}
as.POSIXct(86400, origin="1970-01-01", tz="GMT")
as.POSIXlt(86400, origin="1970-01-01", tz="America/Chicago")
```

>>>>

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags:
- Data science
- Rmarkdown code
source: new
page_update: complete
---

@@

```{r posix-time-01}
date_string <- "1970-01-01"
date_internal_r_format <- as.Date(date_string)
date_posix_ct <- as.POSIXct(date_string)
date_posix_lt <- as.POSIXlt(date_string)

@@

```{r posix-time-02}
print.default(date_string)
```

@@

```{r posix-time-03}
print.default(date_internal_r_format)
```

@@

```{r posix-time-04}
print.default(date_posix_ct)
```

@@

```{r posix-time-05}
print.default(date_posix_lt)
```

@@

```{r posix-time-06}
date_internal_r_format <- as.Date(1, origin="1970-01-01")
date_posix_ct <- as.POSIXct(86400, origin="1970-01-01")
date_posix_lt <- as.POSIXlt(86400, origin="1970-01-01")

@@

```{r posix-time-07}
as.POSIXct(86400, origin="1970-01-01", tz="GMT")
as.POSIXlt(86400, origin="1970-01-01", tz="America/Chicago")
```
